### 2022-08-26 README.Rmd
compressed the publication analysis folder
updated readme

when citing wagglefit please use (insert citation for publication).

## Honey bees vary collective decision making in different landscapes

All code used in the publication (insert citation link) is stored in `inst/publication/`.

>>>>

## Honeybees vary collective decision making in different landscapes

All code used in the publication *Honeybees vary collective decision making in different landscapes* is stored in `inst/publication.tar.gz/`. To extract it use `tar -xzvf publication.tar.gz`.
